### 2018-11-14 arxiv/introduction.tex
First draft of arxiv version of the paper
Intro and reformatting

>>>>

The paper is organized as follows.
In \sec{datasets} we digest into details of both CLEVR and CoGenT datasets, emphasizing their differences.
Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
\sec{experiments} discusses the most important findings when using transfer learning on CLEVR and both versions of CoGenT.
In order to facilitate the lecture we cherry-picked a subset of experiments -- the whole table with comparison of both MAC and S-MAC models when training/fine-tuning/testing MAC and S-MAC models on different datasets can be found in Appendix A.
Additionally, in \sec{failures} we present examples that support our hypotheses on lack of disentanglement of concepts in both models.
\sec{comparison} presents 
We conclude the paper in \sec{conclusion}.
